### 2020-09-17 priority-gv.tex
Restructuring.
Added section headers back in.
More figures!

\subsection{Static Syntax}%
\label{sec:pgv-syntax-static}

\subsubsection{Priorities, types, and environments}
\[
\begin{array}{lcl}
  \cs{o}, \cs{p}, \cs{q}, \cs{r}
  & \in & \mathbb{N}\cup\{\cs{\pbot},\cs{\ptop}\}
  \\
  \ty{S}
  & \coloneqq & \ty{\tysend[\cs{o}]{T}{S}}
    \sep        \ty{\tyrecv[\cs{o}]{T}{S}}
    \sep        \ty{\tyends[\cs{o}]}
    \sep        \ty{\tyendr[\cs{o}]}
  \\
  \ty{T}, \ty{U}
  & \coloneqq & \ty{\tyunit}
    \sep        \ty{\tyvoid}
    \sep        \ty{\typrod{T}{U}}
    \sep        \ty{\tysum{T}{U}}
    \sep        \ty{\tylolli[\cs{p},\cs{q}]{T}{U}}
    \sep        \ty{S}
  \\
  \ty{\Gamma}, \ty{\Delta}
  & \coloneqq & \ty{\emptyenv}
    \sep        \ty{\Gamma}, \tmty{x}{T}
\end{array}
\]
\[
\begin{array}{lcl}
  \ty{\co{\tysend[\cs{o}]{T}{S}}} & = & \ty{\tyrecv[\cs{o}]{T}{\co{S}}}
  \\
  \ty{\co{\tyrecv[\cs{o}]{T}{S}}} & = & \ty{\tysend[\cs{o}]{T}{\co{S}}}
\end{array}
\qquad
\begin{array}{lcl}
  \ty{\co{\tyends[\cs{o}]}} & = & \ty{\co{\tyendr[\cs{o}]}}
  \\
  \ty{\co{\tyendr[\cs{o}]}} & = & \ty{\co{\tyends[\cs{o}]}}
\end{array}
\]
\[
\begin{array}{lcl}
  \pr(\ty{\tysend[\cs{o}]{T}{S}}) & = & \cs{o} \\
  \pr(\ty{\tyrecv[\cs{o}]{T}{S}}) & = & \cs{o} \\
  \\
  \pr(\ty{\typrod{T}{U}}) & = & \pr({\ty{T}})\sqcap\pr({\ty{U}}) \\
  \pr(\ty{\tysum{T}{U}})  & = & \pr({\ty{T}})\sqcap\pr({\ty{U}}) \\
  \pr(\ty{\tylolli[\cs{p},\cs{q}]{T}{U}}) & = & \cs{p} \\
  \\
  \pr(\ty{\Gamma}, \tmty{x}{A}) & = & \pr(\ty{\Gamma})\sqcap\pr(\ty{A})
\end{array}
\qquad
\begin{array}{lcl}
  \pr(\ty{\tyends[\cs{o}]}) & = & \cs{o} \\
  \pr(\ty{\tyendr[\cs{o}]}) & = & \cs{o} \\
  \\
  \pr(\ty{\tyunit})         & = & \ptop \\
  \pr(\ty{\tyvoid})         & = & \ptop \\
  \pr(\ty{S})               & = & \pr(\ty{S}) \\
  \\
  \pr(\ty{\emptyenv})       & = & \ptop
\end{array}
\]

\subsubsection{Terms}%
\label{sec:pgv-syntax-terms}
\[
\begin{array}{lcl}
  \tm{L}, \tm{M}, \tm{N}
  & \coloneqq & \tm{x}
    \sep        \tm{K}
    \sep        \tm{\lambda x.M}
    \sep        \tm{M\;N} \\
  & \sep      & \tm{\unit}
    \sep        \tm{\letunit{M}{N}} \\
  & \sep      & \tm{\pair{M}{N}}
    \sep        \tm{\letpair{x}{y}{M}{N}} \\
  & \sep      & \tm{\inl{M}}
    \sep        \tm{\inr{M}}
    \sep        \tm{\casesum{L}{x}{M}{y}{N}} \\
  & \sep      & \tm{\absurd{M}} \\
  \tm{K}
  & \coloneqq & \tm{\link}
    \sep        \tm{\new}
    \sep        \tm{\spawn}
    \sep        \tm{\send}
    \sep        \tm{\recv}
    \sep        \tm{\wait}
    \sep        \tm{\close}
\end{array}
\]

\subsubsection{Syntactic Sugar}%
\label{sec:pgv-syntax-sugar}

\[
\begin{array}{lcl}
  \ty{\tylolli{T}{U}}
  & \elabarrow & \ty{\tylolli[\cs{\ptop},\cs{\pbot}]{T}{U}} \\
  \ty{\tyselect[\cs{o}]{S}{S'}}
  & \elabarrow & \ty{\tysend[\cs{o}]{(\tysum{\co{S}}{\co{S'}})}{\tyends[\cs{o+1}]}} \\
  \ty{\tyoffer[\cs{o}]{S}{S'}}
  & \elabarrow & \ty{\tyrecv[\cs{o}]{(\tysum{S}{S'})}{\tyendr[\cs{o+1}]}} \\
  \ty{\tyselectemp[\cs{o}]}
  & \elabarrow & \ty{\tysend[\cs{o}]{\tyvoid}{\tyends[\cs{o+1}]}} \\
  \ty{\tyofferemp[\cs{o}]}
  & \elabarrow & \ty{\tyrecv[\cs{o}]{\tyvoid}{\tyendr[\cs{o+1}]}} \\
  \\
  \tm{\andthen{M}{N}}
  & \elabarrow & \tm{\letunit{M}{N}} \\
  \tm{\letbind{x}{M}{N}}
  & \elabarrow & \tm{(\lambda x.N)\;M} \\
  \tm{\lambda\unit.M}
  & \elabarrow & \tm{\lambda z.\letunit{z}{M}} \\
  \tm{\lambda\pair{x}{y}.M}
  & \elabarrow & \tm{\lambda z.\letpair{x}{y}{z}{M}} \\
  \tm{\fork}
  & \elabarrow & \tm{\lambda x.\letpair{y}{z}{\new}{\andthen{\spawn\;{(\lambda\unit.x\;y)}}{z}}} \\
  \tm{\select{\ell}}
  & \elabarrow & \tm{\lambda x.\letpair{y}{z}{\new}{\andthen{\close\;(\send\;{\pair{\ell\;y}{x}})}{z}}} \\
  \multicolumn{3}{l}{\tm{\offer{L}{x}{M}{y}{N}}\elabarrow} \\
  \multicolumn{3}{l}{
  \qquad\tm{\letpair{z}{w}{\recv\;{L}}{\andthen{\wait\;{w}}{\casesum{z}{x}{M}{y}{N}}}}} \\
  \tm{\offeremp{L}}
  & \elabarrow & \tm{\letpair{z}{w}{\recv\;L}{\andthen{\wait\;{w}}{\absurd{z}}}}
\end{array}
\]

\subsection{Static Typing}%
\label{sec:pgv-typing-static}

\subsubsection{Typing Rules}
\begin{mathpar}
  \inferrule*[lab=T-Var]{
  }{\tseq[\cs{\pbot}]{\tmty{x}{T}}{x}{T}}

  \inferrule*[lab=T-Lam]{
    \tseq[\cs{o}]{\ty{\Gamma},\tmty{x}{T}}{M}{U}
  }{\tseq[\cs{\pbot}]{\ty{\Gamma}}{\lambda x.M}{\tylolli[\cs{\pr(\ty{\Gamma})},\cs{o}]{T}{U}}}

  \inferrule*[lab=T-Const]{
  }{\tseq[\cs{\pbot}]{\emptyenv}{K}{T}}

  \inferrule*[lab=T-App]{
    \tseq[\cs{p}]{\ty{\Gamma}}{M}{\tylolli[\cs{o},\cs{r}]{T}{U}}
    \\
    \tseq[\cs{q}]{\ty{\Delta}}{N}{T}
    \\
    \cs{p}<\pr(\ty{\Delta})
    \\
    \cs{q}<\cs{o}
  }{\tseq[\cs{p}\sqcup\cs{q}\sqcup\cs{o}]{\ty{\Gamma},\ty{\Delta}}{M\;N}{U}}
  \\
  \inferrule*[lab=T-Unit]{
  }{\tseq[\cs{\pbot}]{\emptyenv}{\unit}{\tyunit}}

  \inferrule*[lab=T-LetUnit]{
    \tseq[\cs{p}]{\ty{\Gamma}}{M}{\tyunit}
    \\
    \tseq[\cs{q}]{\ty{\Delta}}{N}{T}
    \\
    \cs{p}<\pr(\ty{\Delta})
  }{\tseq[\cs{p}\sqcup\cs{q}]{\ty{\Gamma},\ty{\Delta}}{\letunit{M}{N}}{T}}

  \inferrule*[lab=T-Pair]{
    \tseq[\cs{p}]{\ty{\Gamma}}{M}{T}
    \\
    \tseq[\cs{q}]{\ty{\Delta}}{N}{U}
    \\
    \cs{p}<\pr(\ty{\Delta})
  }{\tseq[\cs{p}\sqcup\cs{q}]{\ty{\Gamma},\ty{\Delta}}{\pair{M}{N}}{\typrod{T}{U}}}

  \inferrule*[lab=T-LetPair]{
    \tseq[\cs{p}]{\ty{\Gamma}}{M}{\typrod{T}{T'}}
    \\
    \tseq[\cs{q}]{\ty{\Delta},\tmty{x}{T},\tmty{y}{T'}}{N}{U}
    \\
    \cs{p}<\pr(\ty{\Delta},\ty{T},\ty{T'})
  }{\tseq[\cs{p}\sqcup\cs{q}]{\ty{\Gamma},\ty{\Delta}}{\letpair{x}{y}{M}{N}}{U}}

  \inferrule*[lab=T-Inl]{
    \tseq[o]{\ty{\Gamma}}{M}{T}
    \\
    \pr(\ty{T})=\pr(\ty{U})
  }{\tseq[o]{\ty{\Gamma}}{\inl{M}}{\tysum{T}{U}}}

  \inferrule*[lab=T-Inr]{
    \tseq[o]{\ty{\Gamma}}{M}{U}
    \\
    \pr(\ty{T})=\pr(\ty{U})
  }{\tseq[o]{\ty{\Gamma}}{\inr{M}}{\tysum{T}{U}}}

  \inferrule*[lab=T-CaseSum]{
    \tseq[\cs{p}]{\ty{\Gamma}}{L}{\tysum{T}{T'}}
    \\
    \tseq[\cs{q}]{\ty{\Delta},\tmty{x}{T}}{M}{U}
    \\
    \tseq[\cs{q}]{\ty{\Delta},\tmty{y}{T'}}{N}{U}
    \\
    \cs{p}<\pr(\ty{\Delta})
  }{\tseq[\cs{p}\sqcup\cs{q}]{\ty{\Gamma},\ty{\Delta}}{\casesum{L}{x}{M}{y}{N}}{U}}

  \inferrule*[lab=T-Absurd]{
    \tseq[o]{\ty{\Gamma}}{M}{\tyvoid}
  }{\tseq[o]{\ty{\Gamma},\ty{\Delta}}{\absurd{M}}{T}}
\end{mathpar}
We write $\tmty{K}{T}$ for $\tseq[\cs{\pbot}]{\emptyenv}{K}{T}$ in typing derivations.

\subsubsection{Type Schemas for Constants}
\begin{mathpar}
  \tmty{\link}{\tylolli{\typrod{S}{\co{S}}}{\tyunit}}

  \tmty{\new}{\tylolli{\tyunit}{\typrod{S}{\co{S}}}}

  \tmty{\spawn}{\tylolli{(\tylolli[\cs{p},\cs{q}]{\tyunit}{\tyunit})}{\tyunit}}
  \\
  \tmty{\send}{\tylolli[\cs{\ptop},\cs{o}]{\typrod{T}{\tysend[\cs{o}]{T}{S}}}{S}}

  \tmty{\recv}{\tylolli[\cs{\ptop},\cs{o}]{\tyrecv[\cs{o}]{T}{S}}{\typrod{T}{S}}}
  \\
  \tmty{\close}{\tylolli[\cs{\ptop},\cs{o}]{\tyends[\cs{o}]}{\tyunit}}

  \tmty{\wait}{\tylolli[\cs{\ptop},\cs{o}]{\tyendr[\cs{o}]}{\tyunit}}
\end{mathpar}

\subsubsection{Typing Rules for Syntactic Sugar}
\begin{mathpar}
  \inferrule*[lab=T-Seq]{
    \tseq[\cs{p}]{\ty{\Gamma}}{M}{\tyunit}
    \\
    \tseq[\cs{q}]{\ty{\Delta}}{N}{T}
    \\
    \cs{p}<\pr(\ty{\Delta})
  }{\tseq[\cs{p}\sqcup\cs{q}]{\ty{\Gamma},\ty{\Delta}}{\andthen{M}{N}}{T}}

  \inferrule*[lab=T-Let]{
    \tseq[\cs{p}]{\ty{\Gamma}}{M}{T}
    \\
    \tseq[\cs{q}]{\ty{\Delta},\tmty{x}{T}}{N}{U}
    \\
    \cs{p}<\pr(\ty{\Delta})
  }{\tseq[\cs{p}\sqcup\cs{q}]{\ty{\Gamma},\ty{\Delta}}{\letbind{x}{M}{N}}{U}}
  \\
  \inferrule*[lab=T-LamUnit]{
    {\tseq[\cs{o}]{\ty{\Gamma}}{M}{T}}
  }{\tseq[\cs{\pbot}]
    {\ty{\Gamma}}
    {\lambda\unit.M}
    {\tylolli[\cs{\pr(\ty{\Gamma})},\cs{o}]{\tyunit}{T}}}

  \inferrule*[lab=T-LamPair]
  {\tseq[\cs{o}]
    {\ty{\Gamma},\tmty{x}{T},\tmty{y}{T'}}
    {M}
    {U}}
  {\tseq[\cs{\pbot}]
    {\ty{\Gamma}}
    {\lambda\pair{x}{y}.M}
    {\tylolli[\cs{\pr(\ty{\Gamma})},\cs{o}]{\typrod{T}{T'}}{U}}}
  \\
  \inferrule*[lab=T-Fork]{
  }{\tseq[\cs{\pbot}]
    {\emptyenv}
    {\fork}
    {\tylolli[]{(\tylolli[\cs{p},\cs{q}]{S}{\tyunit})}{\co{S}}}}
  \\
  \inferrule*[lab=T-Select-Inl]{
    \pr(\ty{S})=\pr(\ty{S'})
  }{\tseq[\cs{\pbot}]{\emptyenv}{\select{\labinl}}{\tylolli[\cs{\ptop},\cs{o}]{\tyselect[\cs{o}]{S}{S'}}{S}}}

  \inferrule*[lab=T-Select-Inr]{
    \pr(\ty{S})=\pr(\ty{S'})
  }{\tseq[\cs{\pbot}]{\emptyenv}{\select{\labinr}}{\tylolli[\cs{\ptop},\cs{o}]{\tyselect[\cs{o}]{S}{S'}}{S'}}}

  \inferrule*[lab=T-Offer]{
    {\tseq[\cs{p}]
      {\ty{\Gamma}}
      {L}
      {\tyoffer[\cs{o}]{S}{S'}}}
    \\
    {\tseq[\cs{q}]
      {\ty{\Delta},\tmty{x}{S}}
      {M}
      {T}}
    \\
    {\tseq[\cs{q}]
      {\ty{\Delta},\tmty{y}{S'}}
      {N}
      {T}}
    \\
    \cs{o}\sqcup\cs{p}<\pr(\ty{\Delta},\ty{S},\ty{S'})
  }{\tseq[\cs{o}\sqcup\cs{p}\sqcup\cs{q}]
    {\ty{\Gamma},\ty{\Delta}}
    {\offer{L}{x}{M}{y}{N}}
    {T}}

  \inferrule*[lab=T-Offer-Absurd]{
    \tseq[\cs{p}]
    {\ty{\Gamma}}
    {L}
    {\tyofferemp[\cs{o}]}
    \\
    \cs{o}\sqcup\cs{p}<\pr(\ty{\Delta})
  }{\tseq[\cs{o}\sqcup\cs{p}]
    {\ty{\Gamma},\ty{\Delta}}
    {\offeremp{L}}
    {T}}
\end{mathpar}

\subsection{Runtime Syntax}%
\label{sec:pgv-syntax-runtime}

\subsubsection{Terms}
\[
\begin{array}[t]{lcl}
  \tm{\conf{C}}, \tm{\conf{D}}, \tm{\conf{E}}
  & \coloneqq & \tm{\phi\;M}
    \sep        \tm{\ppar{\conf{C}}{\conf{D}}}
    \sep        \tm{\res{x}{y}{\conf{C}}}
  \\
  \tm{\phi}
  & \coloneqq & \tm{\main}
    \sep        \tm{\child}
  \\
  \tm{V}, \tm{W}
  & \coloneqq & \tm{\lambda x.M}
    \sep        \tm{\unit}
    \sep        \tm{\pair{M}{N}}
    \sep        \tm{\inl{M}}
    \sep        \tm{\inr{M}}
  \\
  \tm{R}
  & \coloneqq & \tm{\link\;\pair{V}{W}}
    \sep        \tm{\new}
    \sep        \tm{\spawn\;V} \\
  & \sep      & \tm{\send\;\pair{V}{W}}
    \sep        \tm{\recv\;V}
    \sep        \tm{\close\;V}
    \sep        \tm{\wait\;V}
  \\
  \tm{E}
  & \coloneqq & \tm{\hole} \\
  & \sep      & \tm{E\;M}
    \sep        \tm{V\;E} \\
  & \sep      & \tm{\letunit{E}{N}} \\
  & \sep      & \tm{\pair{E}{M}}
    \sep        \tm{\pair{V}{E}}
    \sep        \tm{\letpair{x}{y}{E}{M}} \\
  & \sep      & \tm{\inl{E}}
    \sep        \tm{\inr{E}}
    \sep        \tm{\casesum{E}{x}{M}{y}{N}} \\
  \\
  \tm{\conf{F}}
  & \coloneqq & \tm{\phi\;E}
  \\
  \tm{\conf{G}}
  & \coloneqq & \tm{\hole} \\
  & \sep      & \tm{\ppar{\conf{G}}{\conf{C}}}
    \sep        \tm{\res{x}{y}{\conf{G}}}
\end{array}
\]
\[
\begin{array}{ll}
  \tm{\main}  + \tm{\child} = \tm{\main}
  \\
  \tm{\child} + \tm{\main}  = \tm{\main}
\end{array}
\quad
\begin{array}{ll}
  \tm{\child} + \tm{\child} = \tm{\child}
  \\
  \tm{\main}  + \tm{\main} \; \text{undefined}
\end{array}
\]

\subsection{Runtime Typing}%
\label{sec:pgv-typing-runtime}
\begin{mathpar}
  \inferrule*[lab=T-Main]{
    \tseq[\cs{p}]{\ty{\Gamma}}{M}{T}
  }{\cseq[\main]{\ty{\Gamma}}{\main\;M}}

  \inferrule*[lab=T-Child]{
    \tseq[\cs{p}]{\ty{\Gamma}}{M}{\tyunit}
  }{\cseq[\child]{\ty{\Gamma}}{\child\;M}}

  \inferrule*[lab=T-Res]{
    \cseq[\phi]{\ty{\Gamma},\tmty{x}{S},\tmty{y}{\co{S}}}{\conf{C}}
  }{\cseq[\phi]{\ty{\Gamma}}{\res{x}{y}{\conf{C}}}}

  \inferrule*[lab=T-Par]{
    \cseq[\phi]{\ty{\Gamma}}{\conf{C}}
    \\
    \cseq[\phi']{\ty{\Delta}}{\conf{D}}
  }{\cseq[\phi+\phi']{\ty{\Gamma},\ty{\Delta}}{\ppar{\conf{C}}{\conf{D}}}}
\end{mathpar}

\subsection{Operational semantics}%
\label{sec:pgv-semantics}

\subsubsection{Term reduction}
\begin{mathpar}
  \begin{array}{llcl}
    \LabTirName{E-Lam}  & \tm{(\lambda x.M) \; V}
                        & \tred & \tm{\subst{M}{V}{x}}
    \\
    \LabTirName{E-Unit} & \tm{\letunit{\unit}{M}}
                        & \tred & \tm{M}
    \\
    \LabTirName{E-Pair} & \tm{\letpair{x}{y}{\pair{V}{W}}{M}}
                        & \tred & \tm{\subst{\subst{M}{V}{x}}{W}{y}}
    \\
    \LabTirName{E-Inl}  & \tm{\casesum{\inl{V}}{x}{M}{y}{N}}
                        & \tred & \tm{\subst{M}{V}{x}}
    \\
    \LabTirName{E-Inr}  & \tm{\casesum{\inr{V}}{x}{M}{y}{N}}
                        & \tred & \tm{\subst{N}{V}{y}}
  \end{array}
  \\
  \inferrule*[lab=E-Lift]{
    \tm{M}\tred\tm{M'}
  }{\tm{\plug{E}{M}}\tred\tm{\plug{E}{M'}}}
\end{mathpar}

\subsubsection{Structural congruence}
\begin{mathpar}
  \begin{array}{llcl}
    \LabTirName{SC-LinkSwap}   & \tm{\plug{\conf{F}}{\link\;{\pair{x}{y}}}}
                               & \equiv & \tm{\plug{\conf{F}}{\link\;{\pair{y}{x}}}}
    \\
    \LabTirName{SC-ResLink}    & \tm{\res{x}{y}{(\phi\;\link\;\pair{x}{y})}}
                               & \equiv & \tm{\phi\;\unit}
    \\
    \LabTirName{SC-ResSwap}    & \tm{\res{x}{y}{\conf{C}}}
                               & \equiv & \tm{\res{y}{x}{\conf{C}}}
    \\
    \LabTirName{SC-ResComm}    & \tm{\res{x}{y}{\res{z}{w}{\conf{C}}}}
                               & \equiv & \tm{\res{z}{w}{\res{x}{y}{\conf{C}}}}
    \\
    \LabTirName{SC-ResExt}     & \tm{\res{x}{y}{(\ppar{\conf{C}}{\conf{D}}})}
                               & \equiv & \tm{\ppar{\conf{C}}{\res{x}{y}{\conf{D}}}},
                                          \text{ if }{\tm{x},\tm{y}\notin\fv(\tm{\conf{C}})}
    \\
    \LabTirName{SC-ParNil}     & \tm{\ppar{\conf{C}}{\child{\unit}}}
                               & \equiv & \tm{\conf{C}}
    \\
    \LabTirName{SC-ParComm}    & \tm{\ppar{\conf{C}}{\conf{D}}}
                               & \equiv & \tm{\ppar{\conf{D}}{\conf{C}}}
    \\
    \LabTirName{SC-ParAssoc}   & \tm{\ppar{\conf{C}}{(\ppar{\conf{D}}{\conf{E}})}}
                               & \equiv & \tm{\ppar{(\ppar{\conf{C}}{\conf{D}})}{\conf{E}}}
  \end{array}
\end{mathpar}

\subsubsection{Configuration reduction}
\begin{mathpar}
  \begin{array}{llcl}
    \LabTirName{E-Link}  & \tm{\res{x}{y}{(\ppar{\plug{\conf{F}}{\link\;\pair{w}{x}}}{\conf{C}})}}
                         & \cred & \tm{\ppar{\plug{\conf{F}}{\unit}}{\subst{\conf{C}}{w}{y}}}
    \\
    \LabTirName{E-New}   & \tm{\plug{\conf{F}}{\new\;\unit}}
                         & \cred & \tm{\res{x}{y}{(\plug{\conf{F}}{\pair{x}{y}})}}
    \\
    \LabTirName{E-Spawn} & \tm{\plug{\conf{F}}{\spawn\;V}}
                         & \cred & \tm{\ppar{\plug{\conf{F}}{\unit}}{\child\;V\;\unit}}
    \\
    \LabTirName{E-Send}  & \tm{\res{x}{y}{(\ppar
                           {\plug{\conf{F}}{\send\;{\pair{V}{x}}}}
                           {\plug{\conf{F'}}{\recv\;{y}}})}}
                         & \cred & \tm{\res{x}{y}{(\ppar
                                   {\plug{\conf{F}}{x}}
                                   {\plug{\conf{F'}}{\pair{V}{y}}})}}
    \\
    \LabTirName{E-Close} & \tm{\res{x}{y}{(\ppar
                           {\plug{\conf{F}}{\wait\;{x}}}
                           {\plug{\conf{F'}}{\close\;{y}}})}}
                         & \cred & \tm{\ppar{\plug{\conf{F}}{\unit}}{\plug{\conf{F'}}{\unit}}}
  \end{array}
  \\
  \inferrule*[lab=E-LiftC]{
    \tm{\conf{C}}\cred\tm{\conf{C'}}
  }{\tm{\plug{\conf{G}}{\conf{C}}}\cred\tm{\plug{\conf{G}}{\conf{C'}}}}

  \inferrule*[lab=E-LiftM]{
    \tm{M}\tred\tm{M'}
  }{\tm{\plug{\conf{F}}{M}}\tred\tm{\plug{\conf{F}}{M'}}}

  \inferrule*[lab=E-LiftSC]{
    \tm{\conf{C}}\equiv\tm{\conf{C'}}
    \\
    \tm{\conf{C'}}\cred\tm{\conf{D'}}
    \\
    \tm{\conf{D'}}\equiv\tm{\conf{D}}
  }{\tm{\conf{C}}\cred\tm{\conf{D}}}
\end{mathpar}

@@

>>>>

\subsection{Syntax}

\paragraph*{Priorities, types, and environments}
\[
  \cs{o}, \cs{p}, \cs{q}, \cs{r} \in \mathbb{N}\cup\{\cs{\pbot},\cs{\ptop}\}
\]
\[
\begin{array}{lcl}
  \ty{S}
  & \coloneqq & \ty{\tysend[\cs{o}]{T}{S}}
    \sep        \ty{\tyrecv[\cs{o}]{T}{S}}
    \sep        \ty{\tyends[\cs{o}]}
    \sep        \ty{\tyendr[\cs{o}]}
  \\
  \ty{T}, \ty{U}
  & \coloneqq & \ty{\tyunit}
    \sep        \ty{\tyvoid}
    \sep        \ty{\typrod{T}{U}}
    \sep        \ty{\tysum{T}{U}}
    \sep        \ty{\tylolli[\cs{p},\cs{q}]{T}{U}}
    \sep        \ty{S}
  \\
  \ty{\Gamma}, \ty{\Delta}
  & \coloneqq & \ty{\emptyenv}
    \sep        \ty{\Gamma}, \tmty{x}{T}
\end{array}
\]
\[
\begin{array}{lcl}
  \ty{\co{\tysend[\cs{o}]{T}{S}}} & = & \ty{\tyrecv[\cs{o}]{T}{\co{S}}} \\
  \ty{\co{\tyrecv[\cs{o}]{T}{S}}} & = & \ty{\tysend[\cs{o}]{T}{\co{S}}}
\end{array}
\qquad
\begin{array}{lcl}
  \ty{\co{\tyends[\cs{o}]}} & = & \ty{\co{\tyendr[\cs{o}]}} \\
  \ty{\co{\tyendr[\cs{o}]}} & = & \ty{\co{\tyends[\cs{o}]}}
\end{array}
\]
\[
\begin{array}{lcl}
  \pr(\ty{\tysend[\cs{o}]{T}{S}}) & = & \cs{o} \\
  \pr(\ty{\tyrecv[\cs{o}]{T}{S}}) & = & \cs{o} \\
  \pr(\ty{\typrod{T}{U}}) & = & \pr({\ty{T}})\sqcap\pr({\ty{U}}) \\
  \pr(\ty{\tysum{T}{U}})  & = & \pr({\ty{T}})\sqcap\pr({\ty{U}}) \\
  \pr(\ty{\tylolli[\cs{p},\cs{q}]{T}{U}}) & = & \cs{p} \\
  \pr(\ty{\Gamma}, \tmty{x}{A}) & = & \pr(\ty{\Gamma})\sqcap\pr(\ty{A})
\end{array}
\qquad
\begin{array}{lcl}
  \pr(\ty{\tyends[\cs{o}]}) & = & \cs{o} \\
  \pr(\ty{\tyendr[\cs{o}]}) & = & \cs{o} \\
  \pr(\ty{\tyunit})         & = & \ptop \\
  \pr(\ty{\tyvoid})         & = & \ptop \\
  \pr(\ty{S})               & = & \pr(\ty{S}) \\
  \pr(\ty{\emptyenv})       & = & \ptop
\end{array}
\]

\paragraph*{Syntactic Sugar for Types}
\[
  \ty{\tylolli{T}{U}} \elabarrow \ty{\tylolli[\cs{\ptop},\cs{\pbot}]{T}{U}}
\]

\paragraph*{Static Term Syntax}
\[
\begin{array}{lcl}
  \tm{L}, \tm{M}, \tm{N}
  & \coloneqq & \tm{x}
    \sep        \tm{K}
    \sep        \tm{\lambda x.M}
    \sep        \tm{M\;N} \\
  & \sep      & \tm{\unit}
    \sep        \tm{\letunit{M}{N}} \\
  & \sep      & \tm{\pair{M}{N}}
    \sep        \tm{\letpair{x}{y}{M}{N}} \\
  & \sep      & \tm{\inl{M}}
    \sep        \tm{\inr{M}}
    \sep        \tm{\casesum{L}{x}{M}{y}{N}} \\
  & \sep      & \tm{\absurd{M}} \\
  \tm{K}
  & \coloneqq & \tm{\link}
    \sep        \tm{\new}
    \sep        \tm{\spawn}
    \sep        \tm{\send}
    \sep        \tm{\recv}
    \sep        \tm{\wait}
    \sep        \tm{\close}
\end{array}
\]

\paragraph*{Syntactic Sugar for Terms}
\[
\begin{array}{lcl}
  \tm{\andthen{M}{N}}
  & \elabarrow & \tm{\letunit{M}{N}} \\
  \tm{\letbind{x}{M}{N}}
  & \elabarrow & \tm{(\lambda x.N)\;M} \\
  \tm{\lambda\unit.M}
  & \elabarrow & \tm{\lambda z.\letunit{z}{M}} \\
  \tm{\lambda\pair{x}{y}.M}
  & \elabarrow & \tm{\lambda z.\letpair{x}{y}{z}{M}} \\
  \tm{\fork}
  & \elabarrow & \tm{\lambda x.\letpair{y}{z}{\new}{\andthen{\spawn\;{(\lambda\unit.x\;y)}}{z}}}
\end{array}
\]

\paragraph*{Syntactic Sugar for Internal and External Choice}
\[
\begin{array}{lcl}
  \ty{\tyselect[\cs{o}]{S}{S'}}
  & \elabarrow & \ty{\tysend[\cs{o}]{(\tysum{\co{S}}{\co{S'}})}{\tyends[\cs{o+1}]}} \\
  \ty{\tyoffer[\cs{o}]{S}{S'}}
  & \elabarrow & \ty{\tyrecv[\cs{o}]{(\tysum{S}{S'})}{\tyendr[\cs{o+1}]}} \\
\end{array}
\qquad
\begin{array}{lcl}
  \ty{\tyselectemp[\cs{o}]}
  & \elabarrow & \ty{\tysend[\cs{o}]{\tyvoid}{\tyends[\cs{o+1}]}} \\
  \ty{\tyofferemp[\cs{o}]}
  & \elabarrow & \ty{\tyrecv[\cs{o}]{\tyvoid}{\tyendr[\cs{o+1}]}} \\
\end{array}
\]
\[
\begin{array}{lcl}
  \tm{\select{\ell}}
  & \elabarrow & \tm{\lambda x.\letpair{y}{z}{\new}{\andthen{\close\;(\send\;{\pair{\ell\;y}{x}})}{z}}} \\
  \multicolumn{3}{l}{\tm{\offer{L}{x}{M}{y}{N}}\elabarrow} \\
  \multicolumn{3}{l}{
  \qquad\tm{\letpair{z}{w}{\recv\;{L}}{\andthen{\wait\;{w}}{\casesum{z}{x}{M}{y}{N}}}}} \\
  \tm{\offeremp{L}}
  & \elabarrow & \tm{\letpair{z}{w}{\recv\;L}{\andthen{\wait\;{w}}{\absurd{z}}}}
\end{array}
\]

\paragraph*{Runtime Term Syntax}
\[
\begin{array}[t]{lcl}
  \tm{\conf{C}}, \tm{\conf{D}}, \tm{\conf{E}}
  & \coloneqq & \tm{\phi\;M}
    \sep        \tm{\ppar{\conf{C}}{\conf{D}}}
    \sep        \tm{\res{x}{y}{\conf{C}}}
  \\
  \tm{\phi}
  & \coloneqq & \tm{\main}
    \sep        \tm{\child}
  \\
  \tm{V}, \tm{W}
  & \coloneqq & \tm{\lambda x.M}
    \sep        \tm{\unit}
    \sep        \tm{\pair{M}{N}}
    \sep        \tm{\inl{M}}
    \sep        \tm{\inr{M}}
  \\
  \tm{R}
  & \coloneqq & \tm{\link\;\pair{V}{W}}
    \sep        \tm{\new}
    \sep        \tm{\spawn\;V} \\
  & \sep      & \tm{\send\;\pair{V}{W}}
    \sep        \tm{\recv\;V}
    \sep        \tm{\close\;V}
    \sep        \tm{\wait\;V}
  \\
  \tm{E}
  & \coloneqq & \tm{\hole} \\
  & \sep      & \tm{E\;M}
    \sep        \tm{V\;E} \\
  & \sep      & \tm{\letunit{E}{N}} \\
  & \sep      & \tm{\pair{E}{M}}
    \sep        \tm{\pair{V}{E}}
    \sep        \tm{\letpair{x}{y}{E}{M}} \\
  & \sep      & \tm{\inl{E}}
    \sep        \tm{\inr{E}}
    \sep        \tm{\casesum{E}{x}{M}{y}{N}} \\
  \\
  \tm{\conf{F}}
  & \coloneqq & \tm{\phi\;E}
  \\
  \tm{\conf{G}}
  & \coloneqq & \tm{\hole} \\
  & \sep      & \tm{\ppar{\conf{G}}{\conf{C}}}
    \sep        \tm{\res{x}{y}{\conf{G}}}
\end{array}
\]
\[
\begin{array}{ll}
  \tm{\main}  + \tm{\child} = \tm{\main}
  \\
  \tm{\child} + \tm{\main}  = \tm{\main}
\end{array}
\quad
\begin{array}{ll}
  \tm{\child} + \tm{\child} = \tm{\child}
  \\
  \tm{\main}  + \tm{\main} \; \text{undefined}
\end{array}
\]

\subsection{Typing}
\input{fig/pgv-typing}
See \cref{fig:pgv-typing}.

\subsection{Operational Semantics}
\input{fig/pgv-operational-semantics}
See \cref{fig:pgv-operational-semantics}.

@@

\begin{corollary}[Closed Progress, $\cred$]
  \label{thm:pgv-closed-progress-confs}
  If $\cseq[\phi]{\ty{\Gamma}}{\conf{C}}$, then either:
  \begin{description}[labelwidth=8ex]
  \item[Done]
    There exists some $\tm{V}$ such that $\tm{\conf{C}}=\tm{\phi\;V}$;
  \item[Step]
    There exists some $\tm{\conf{D}}$ such that $\tm{\conf{C}} \cred \tm{\conf{D}}$; or
  \end{description}
\end{corollary}
